Constraint Grammar as a SAT problem

### 2015-06-01 paper/nodalida2015.tex
small fixes

\todo{make this nicer: Constraint Grammar (CG)
  \cite{karlsson1995constraint} is a relatively young formalism.
In this work, we implement CG using a SAT solver,
thus relating CG to a wider context in the theory of computation.
This is attractive from several reasons: formal logic is
well-studied, and serves as an abstract language to reason about the
properties of CG. Constraint rules encoded in logic capture richer
dependencies between the tags than standard CG.}

@@

\todo{Our work is inspired by \cite{lager98}, which presents constraint rules as a disjunctive logic program,
and \cite{lager_nivre01}, which reconstructs 4 different formalisms from a logical point of view.
\cite{lindberg_eineborg98ilp,asfrent14} use Inductive Logic Programming to learn CG rules from a tagged corpus.
We explore different approaches to ordering. In the case of unordered
rules, it resembles Finite-State Intersection Grammar \cite{koskenniemi90}.
See also \cite{lager01transformation} for discussion of ordering of
the CG rules.}

@@

We thank Tino Didriksen, Eckhard Bick, Francis Tyers and Anssi
Yli-Jyr{\"a} for comments and suggestions, as well as the anonymous
reviewers and everyone who participated in the discussion at the CG workshop.

>>>>

Constraint Grammar (CG) \cite{karlsson1995constraint} is a relatively
young formalism. It belongs to the reductionist family of parsing
strategies, along with Finite-State Intersection Grammar (FSIG) \cite{koskenniemi90}.
In this work, we use a SAT solver to implement a version of CG that is
roughly compatible with CG-2.
This is attractive from several reasons: formal logic is
well-studied, and serves as an abstract language to reason about the
properties of CG. Constraint rules encoded in logic capture richer
dependencies between the tags than standard CG.

@@

Our work is inspired by \cite{lager98}, which presents constraint
rules as a disjunctive logic program, and \cite{lager_nivre01}, which
reconstructs four different formalisms in first-order logic.
\cite{lindberg_eineborg98ilp} and \cite{asfrent14} use Inductive Logic Programming to learn CG rules from a tagged corpus.
We explore different approaches to ordering. In the case of unordered
rules, it resembles Finite-State Intersection Grammar \cite{koskenniemi90}.
See also \cite{lager01transformation} for discussion of ordering of
the CG rules.

@@

We thank Eckhard Bick, Tino Didriksen, Francis Tyers and Anssi
Yli-Jyr{\"a} for comments and suggestions, as well as the anonymous
reviewers and everyone who participated in the discussion at the CG workshop.
